% ---------
%  Compile with "pdflatex hw0".
% --------
%!TEX TS-program = pdflatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt]{article}
\usepackage{jeffe,handout,graphicx}
\usepackage[utf8]{inputenc}		% Allow some non-ASCII Unicode in source

%  Redefine suits
\usepackage{pifont}
\def\Spade{\text{\ding{171}}}
\def\Heart{\text{\textcolor{Red}{\ding{170}}}}
\def\Diamond{\text{\textcolor{Red}{\ding{169}}}}
\def\Club{\text{\ding{168}}}

\def\Cdot{\mathbin{\text{\normalfont \textbullet}}}
\def\Sym#1{\textbf{\texttt{\color{BrickRed}#1}}}
\newcommand{\comp}[1]{#1_{\text{comp}}}

\newtheorem{Lemma}{lemma}
\newcommand{\IsSinL}{\text{IsStringInL}}

\usepackage{tikz}
\usetikzlibrary{automata, positioning}
\usepackage{listings}

% =====================================================
%   Define common stuff for solution headers
% =====================================================
\Class{CS/ECE 374}
\Semester{Spring 2017}
\Authors{3}
\AuthorOne{Lanxiao Bai}{lbai5}
\AuthorTwo{Renheng Ruan}{rruan2}
\AuthorThree{Ho Yin Au}{hoyinau2}
%\Section{}

% =====================================================
\begin{document}

% ---------------------------------------------------------


\HomeworkHeader{10}{1}	% homework number, problem number

\begin{quote}
	Given an undirected graph $G=(V,E)$ a {\em matching} in $G$ is
  a set of edges $M \subseteq E$ such that no two edges in $M$ share
  a node. A matching $M$ is {\em perfect} if $2|M| = |V|$, in other words
  if every node is incident to some edge of $M$. PerfectMatching is
  the following decision problem: does a given graph $G$ have a perfect
  matching? Describe a polynomial-time reduction from PerfectMatching to
  SAT. Does this problem that PerfectMatching is a difficult problem?
\end{quote}
\hrule

\begin{solution}
	First of all we can easily check if $2|M| = |V|$ is true if given an answer in linear time $O(1)$, thus the problem is in NP.
	
	Then we can give a construct to reduce PerfectMatch to SAT:
	
	\begin{itemize}
		\item For each $v \in V$, encode $v$ as $c(v) \in \{0, 1\}$, then PerfectMatch requires that there is a set of code $c(v_i)$ for all $v_i \in V$ that makes
		
		\[\bigwedge_{v_i \in V} (\bigvee_{v_j \in adj(v_i) - \{v_i\}} (v_i \wedge v_j) \wedge (\bigwedge_{v_k \in adj(v_i) - \{v_i, v_j\}} (v_i \wedge \neg v_k) )) = 1\]
		
		to be true, which is essentially the SAT problem.
	\end{itemize}
	
	How we claim that PerfectMatch returns true if SAT returns true and PerfectMatch returns false if SAT returns false.
	
	\paragraph{Proof:}
	"$\Rightarrow$":
	
	When there is a PerfectMatch for $G = (V, E)$, then for any given $v_i$, there is exactly $1$ points that has the same code as it, so
		
		\[\bigvee_{v_j \in adj(v_i) - \{v_i\}} (v_i \wedge v_j) \wedge (\bigwedge_{v_k \in adj(v_i) - \{v_i, v_j\}} (v_i \wedge \neg v_k) ) = 1\]
		
		which gives that 
		
		\[\bigwedge_{v_i \in V} (\bigvee_{v_j \in adj(v_i) - \{v_i\}} (v_i \wedge v_j) \wedge (\bigwedge_{v_k \in adj(v_i) - \{v_i, v_j\}} (v_i \wedge \neg v_k) )) = 1\]
		
		"$\Leftarrow$":
		
		When 
		
		\[\bigwedge_{v_i \in V} (\bigvee_{v_j \in adj(v_i) - \{v_i\}} (v_i \wedge v_j) \wedge (\bigwedge_{v_k \in adj(v_i) - \{v_i, v_j\}} (v_i \wedge \neg v_k) )) = 1\]
		
		for any given $v_i$, there is exactly $1$ points that has the same code with it, so
		
		\[\bigvee_{v_j \in adj(v_i) - \{v_i\}} (v_i \wedge v_j) \wedge (\bigwedge_{v_k \in adj(v_i) - \{v_i, v_j\}} (v_i \wedge \neg v_k) ) = 1\]
		
		which means at least one encoding makes 
		
		\[(v_i \wedge v_j) \wedge (\bigwedge_{v_k \in adj(v_i) - \{v_i, v_j\}} (v_i \wedge \neg v_k) = 1\]
		
		so for $G = (V, E)$, then for any given $v_i$, there is exactly $1$ points that has the same code as it.
		
		Hence, we conclude that PerfectMatch returns true if SAT returns true and PerfectMatch returns false if SAT returns false.
		
		Since SAT Problem is a NP-Complete Problem, PerfectMatch is harder than SAT, so PerfectMatch is a difficult problem.
		
			
\end{solution}
\clearpage

\end{document}
