% ---------
%  Compile with "pdflatex hw0".
% --------
%!TEX TS-program = pdflatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt]{article}
\usepackage{jeffe,handout,graphicx}
\usepackage[utf8]{inputenc}		% Allow some non-ASCII Unicode in source

%  Redefine suits
\usepackage{pifont}
\def\Spade{\text{\ding{171}}}
\def\Heart{\text{\textcolor{Red}{\ding{170}}}}
\def\Diamond{\text{\textcolor{Red}{\ding{169}}}}
\def\Club{\text{\ding{168}}}

\def\Cdot{\mathbin{\text{\normalfont \textbullet}}}
\def\Sym#1{\textbf{\texttt{\color{BrickRed}#1}}}
\newcommand{\comp}[1]{#1_{\text{comp}}}

\newtheorem{Lemma}{lemma}
\newcommand{\IsSinL}{\text{IsStringInL}}

\usepackage{tikz}
\usetikzlibrary{automata, positioning}
\usepackage{listings}

% =====================================================
%   Define common stuff for solution headers
% =====================================================
\Class{CS/ECE 374}
\Semester{Spring 2017}
\Authors{3}
\AuthorOne{Lanxiao Bai}{lbai5}
\AuthorTwo{Renheng Ruan}{rruan2}
\AuthorThree{Ho Yin Au}{hoyinau2}
%\Section{}

% =====================================================
\begin{document}

% ---------------------------------------------------------


\HomeworkHeader{6}{1}	% homework number, problem number

\begin{quote}
	The McKing chain wants to open several restaurants along Red
  street in Shampoo-Banana. The possible locations are at $L_1,L_2,
  \ldots, L_n$ where $L_i$ is at distance $m_i$ meters from the start
  of Red street. Assume that the street is a straight line and the
  locations are in increasing order of distance from the starting
  point (thus $0 \leq m_1 < m_2 < \ldots < m_n$). McKing has collected
  some data indicating that opening a restaurant at location $L_i$
  will yield a profit of $p_i$ independent of where the other
  restaurants are located. However, the city of Shampoo-Banana has a
  zoning law which requires that any two McKing locations should be
  $D$ or more meters apart. {\em In addition McKing does not want to
    open more than $k$ restaurants due to budget constraints.}
  Describe an algorithm that McKing can use to figure out the maximum
  profit it can obtain by opening restaurants while satisfying the
  city's zoning law and the constraint of opening at most $k$
  restaurants.  Your algorithm should use only $O(n)$ space.
\end{quote}
\hrule

\begin{solution}
	Consider a location $L_i$ on Red Street, McKing can either open a restaurant or not, depends on which way it can reach the maximum of profits while the rest is already the optimum solution. 
	
	As a result, if we suppose their is a routine \textsc{Next}(i) that gives the minimum next $i$ that $L_{\textsc{Next}(i)}$ can open a restaurant if a restaurant is opened at $L_i$, the max profit $\textsc{MaxProfits}$ is as following:
	
	\[\textsc{MaxProfit}(\textit{i}) = 
		\begin{cases}
			0 & \text{if }i > n \text{ or } k \leq 0\\
			\max \begin{cases}
					p_i + \textsc{MaxProfit}(\textsc{Next}(\textit{i}), k - 1)\\
					\textsc{MaxProfit}(\textit{i} + 1, k)
				 \end{cases} & \text{if } i \leq n \text{ and } k > 0
		\end{cases} \]
		
	Although we use two parameters to the function, 1-D array of only with length of $n$ is enough to memoize the result, since we can use $k$ to count down.
	
	As a result, $\textsc{MaxProfits}(i)$ only depends on $\textsc{MaxProfits}(i + 1)$, so we can design a iterative algorithm to fill in the 1-D array as the following.
	
	\begin{center}
		\begin{algorithm}
			\textul{$\textsc{GetMaxProfit}(\textit{L}[1\, .. \, n], p[1\, ..\, n], k)$:}\+
			\\\textsc{MaxProfit}[n] = p[n]
			\\maximum $\gets \textsc{MaxProfit}[n]$
			\\for $i \gets n - 1$ to $1$\+
			\\ if k < $0$\+
			\\	return maximum\-
			\\	profit1 = \textsc{MaxProfit}[\textsc{Next}(i)] + p[i]
			\\ profit2 = \textsc{MaxProfit}[$i+1$] 
			\\ if profit1 > profit2\+
			\\	$k \gets k - 1$\-
			\\ \textsc{MaxProfit}[i] $\gets$ max\{profit1, profit2\}
			\\ maximum $\gets$ $\textsc{MaxProfit}[i]$\-
			\\ return maximum
			
		\end{algorithm}
	\end{center}
	
	Obviously, this algorithm takes $O(n)$ space to execute, since the data is memoized by a 1-D array. And since the result can be given with a loop of at most the length of $n$, the time complexity depends on the time complexity of $\textsc{Next}(i)$, which can take $O(\log n)$ to execute since $m_i$ is sorted and, as a result, binary search can be used. Hence, the overall time complexity is $O(n \log n)$. 
\end{solution}
\clearpage

\end{document}
