% ---------
%  Compile with "pdflatex hw0".
% --------
%!TEX TS-program = pdflatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt]{article}
\usepackage{jeffe,handout,graphicx}
\usepackage[utf8]{inputenc}		% Allow some non-ASCII Unicode in source

%  Redefine suits
\usepackage{pifont}
\def\Spade{\text{\ding{171}}}
\def\Heart{\text{\textcolor{Red}{\ding{170}}}}
\def\Diamond{\text{\textcolor{Red}{\ding{169}}}}
\def\Club{\text{\ding{168}}}

\def\Cdot{\mathbin{\text{\normalfont \textbullet}}}
\def\Sym#1{\textbf{\texttt{\color{BrickRed}#1}}}
\newcommand{\comp}[1]{#1_{\text{comp}}}

\newtheorem{Lemma}{lemma}
\newcommand{\IsSinL}{\text{IsStringInL}}

\usepackage{tikz}
\usetikzlibrary{automata, positioning}
\usepackage{listings}

% =====================================================
%   Define common stuff for solution headers
% =====================================================
\Class{CS/ECE 374}
\Semester{Spring 2017}
\Authors{3}
\AuthorOne{Lanxiao Bai}{lbai5}
\AuthorTwo{Renheng Ruan}{rruan2}
\AuthorThree{Ho Yin Au}{hoyinau2}
%\Section{}

% =====================================================
\begin{document}

% ---------------------------------------------------------


\HomeworkHeader{9}{1}	% homework number, problem number

\begin{quote}
	Red street in the city Shampoo-Banana can be modeled as a
  straight line starting at $0$.  The street has $n$ houses at
  locations $x_1,x_2,\ldots,x_n$ on the line. The local cable company
  wants to install some new fiber optic equipment at several locations
  such that every house is within distance $r$ from one of the
  equipment locations. The city has granted permits to install the
  equipment, but only at some $m$ locations on the street given y
  locations $y_1,y_2, \ldots,y_m$. For simplicity assume that all the
  $x$ and $y$ values are distinct. You can also assume that
  $x_1 < x_2 < \ldots < x_n$ and that $y_1 < y_2 < \ldots < y_m$.
  \begin{itemize}
  \item Describe a greedy algorithm that finds the minimum number of
    equipment locations that the cable company can build to satisfy
    the desired constraint that every house is within distance $r$
    from one of them.  Your algorithm has to detect if a feasible
    solution does not exist. Prove the correctness of the
    algorithm. One way to do this by arguing that there is an optimum
    solution that agrees with the first choice of your greedy
    algorithm.
    \end{itemize}
\end{quote}
\hrule

\begin{solution}
	Greedy strategy: Take the largest $i$ that location $y[i]$ that $|y[i] - x[1]| < r$, discard all $x[j] \in [y[i] - r, y[i] + r]$, discard $y[i]$ for all $i \leq y$ and recurse.
	
	\textbf{Proof:}
		Suppose we take $y[j]$ that $j < i$ and $|y[j] - x[1]| < r$, then if there is some $x \in [y[j] + r, y[i] + r]$ other than $x[1]$, there needs at least one more $y$ to cover these $x$. 
		
		Since $i$ is the largest $i$ that location $y[i]$ that $|y[i] - x[1]| < r$, it is impossible to take $y[j]$ that $j > i$ while still cover $x[1]$.
		
		Hence, we conclude that take $y[i]$ has the optimum substructure, and by induction the greedy strategy is correct.
		
\end{solution}
\clearpage

\end{document}
