\documentclass[12pt]{article}
\title{Software Engineering I}
\date{\today}
\author{Lanxiao Bai}

%-----------Packeges---------------%
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{tocloft}
\usepackage{float}
\usepackage{graphicx}
\usepackage[bookmarks=true]{hyperref}
\usepackage{fancyhdr}


%----------Definition & Theorem----%
\newtheorem{definition}{Definition}[subsection]
\newtheorem{theorem}{Theorem}[subsection]
\newtheorem{proposition}{Proposition}[subsection]
\newtheorem{lemma}{Lemma}[subsection]
\newtheorem{corollary}{Corollary}[subsection]


\pagestyle{fancy}
\fancyhead[L]{CS 427}
\fancyhead[C]{Note}
\fancyhead[R]{Lanxiao Bai}

\begin{document}
\maketitle
\newpage
\tableofcontents
\newpage

\section{Bug Reporting}
\subsection{Key Elements of Bug Reporting:}
\begin{itemize}
    \item Reproduce - Test it again
    \item Isolate - Test it differently
    \item Generalize - Test it elsewhere
\end{itemize}
\subsubsection{Reproduce}
    \begin{itemize}
        \item Three times would be good enough.
        \item Document the platform, environment and sequence of actions that would trigger the bug.
    \end{itemize}

\subsubsection{Isolate}
    \begin{itemize}
        \item Change the variables
            \begin{itemize}
                \item Make changes one at a time
                \item Require thought and knowledge of system under test(SUT)
                \item May not be immediate obvious
            \end{itemize}
        \item Can be an extensive process
            \begin{itemize}
                \item Match amount of effort to severity of problem
                \item Unavoidable if it's your job
            \end{itemize}
    \end{itemize}

\subsubsection{Generalize}
    \begin{itemize}
        \item Look for related failures in SUT
        \item Avoid confusing unrelated problems 
    \end{itemize}
\subsection{Terminology}
    \begin{itemize}
        \item Programmer makes \textbf{mistake}.
        \item \textbf{Fault, defect, bug} happen in program.
        \item Program \textbf{fail} during execution
        \item \textbf{Error} Dirrentce between output with expectation.
    \end{itemize}
    
\section{Software Configuration Management (SCM)}
\begin{itemize}
    \item Change control
    \item Version Control
    \item Building
    \item Releasing
\end{itemize}

\subsection{Version Control System (VCS)}
\begin{definition}
    A Version Control System is a software system that keeps track of the changes made to a set of files so that you can recall a specific version.
\end{definition}

    With VCS, you can: 
    \begin{itemize}
        \item Collaborate
        \item Revert changes
        \item Go back to a specific version
    \end{itemize}

    \paragraph{Typical workflow: } repo $\rightarrow$ check out $\rightarrow$ hack $\rightarrow$ check in
    \paragraph{Problem:} If multiple people are changing the same software?
    \begin{itemize}
        \item Locking? - Impossible, or people have to wait.
        \item Merging? - Risky, maybe introduce bugs.
    \end{itemize}

\subsection{Build(Maven)}
    \paragraph{Things to consider:}
    \begin{itemize}
        \item Which compiler? Which flags?
        \item Which source file?
        \item Which libs?
        \item Which version?
    \end{itemize}
    
    \paragraph{Tools:}
    \begin{itemize}
        \item make - Under Unix, original tool
        \item ant - Java based, uses XML
        \item Maven - Used by $\mathbb{K}$
        \item ...
    \end{itemize}

    \subsection{Testing and JUnit}
    
    \paragraph{Why test?}
    \begin{itemize}
        \item Improve quality
        \item Measure quality
        \item Learn the software
    \end{itemize}
    
    \paragraph{What is a test?}
    \begin{itemize}
        \item Run program with known inputs, check results
        \item Test can document faults
        \item Test can document code
    \end{itemize}

    \paragraph{What kind of test?}
    \begin{itemize}
        \item Programmer / Non=programmer
        \item Developer / Tester
        \item Unit test / Integration tests / Functional tests / System tests
        \item Automated/ manual
    \end{itemize}
\subsection{Software Production}
    \paragraph{Product} = set of components/documents
        \begin{itemize}
            \item Codes
            \item Docs
            \item Tests
            \item Designs
            \item Requirements
            \item ... 
        \end{itemize}

    \paragraph{You need to} keep track of:
        \begin{itemize}
            \item Version
                \begin{itemize}
                    \item Sequence if versions during development
                    \begin{itemize}
                        \item Alpha/Beta/Final release...
                    \end{itemize}
                    \item Different released versions
                    \item branch
                    \begin{itemize}
                        \item Traditional VC: Avoid
                        \item Modern: Encourage use of short lived branches
                        \item Good reasons to branch
                            \begin{itemize}
                                \item Fix bugs
                                \item Experiment version
                                \item Political fight
                            \end{itemize}
                        \item Bad reasons to branch
                            \begin{itemize}
                                \item Support different platform (Make subclasses / use conditional compilation / make portability library instead)
                                \item Support different customer
                            \end{itemize}
                    \end{itemize}
                \end{itemize}
            \item Resources
                \begin{itemize}
                    \item Test suites
                    \item Manual
                    \item User cases
                    \item Designs
                \end{itemize}
        \end{itemize}
    \paragraph{Baseline}Baseline is a software configuration item that has been reviewed and agreed upon, and that can be changed only through formal change control procedures
    
    \paragraph{Control}Authority management
    
    \subsection{Release} Release is a software configuration item that the developers give to other people. Release should be a baseline.
    
    \section{Extreme Programming(XP)}
    \subsection{Modified Waterfall}
    	\begin{enumerate}
    		\item Requirement, analysis
    		\item Design, Checking
    		\item Implementation, unit testing
    		\item Integration, System Testing
    		\item Maintenance
    	\end{enumerate}
   \subsection{XP}
   		\paragraph{Big ideas}
   		\begin{itemize}
   			\item Don't write much docs
   			\item Implement features one by one
   			\item Release code frequently
   			\item Work closely with the customer
   			\item Communicate a lot with team members
   		\end{itemize}
   		
   		\paragraph{Activities}
   		\begin{itemize}
   			\item Requirement, analysis - Planning game
    		\item Design, Checking - Test-driven development
    		\item Implementation, unit testing - Refactoring for design 
    		\item Development - Pair Programming
    		\item Integration - Continous integration
   		\end{itemize}
\end{document}

